---
title: "Cloze Project Data Analysis"
output: html_notebook
---
```{r setup, include=FALSE}

```

```{r}
knitr::opts_chunk$set(echo = TRUE)
suppressPackageStartupMessages(library(Rmisc))
suppressPackageStartupMessages(library(data.table))
suppressPackageStartupMessages(library(stringr))
suppressPackageStartupMessages(library(dplyr))
suppressPackageStartupMessages(library(ggplot2))
suppressPackageStartupMessages(library(lme4))
suppressPackageStartupMessages(library(gridExtra))
suppressPackageStartupMessages(library(tidyr))
suppressPackageStartupMessages(library(optimx))
suppressPackageStartupMessages(library(car))
```

```{r}
data <- read.csv('../data/PreprocessedData.csv')
data$ClausePlacement <- as.factor(data$ClausePlacement)
data$Location <- as.factor(data$Location)
summary(data)
```
Load and summarize the data. We also want to switch the data types of 
ClausePlacement and Location to categorical since they are just binary factors

```{r}
data <- data %>%
  mutate(Target = case_when(
    Location == 'Original' ~ Target,
    Location == 'Replacement' ~ NA
  )) %>%
  fill(Target, .direction='down')

data <- data %>%
  mutate(ResponseIsTarget = Response == Target)
summary(data)
```
We need to an additional column ResponseIsTarget, which 
indicates whether the participants gave Target or not.

```{r}
contrasts.Tri <- 
  matrix(c(1/2, 1/2,
           -1, 1), 
         ncol = 2) %>%
  t(.) %>%
  solve(.) %>%
  .[,2:2]

contrasts(data$ClausePlacement) <- contrasts.Tri
contrasts(data$Location) <- c(-.5,.5)

model_matrix <- model.matrix( ~ ClausePlacement * Location, data)

data$cp1 <- model_matrix[,2]
data$l1 <- model_matrix[,3]
summary(data)
```
Setting up our contrasts

```{r}
model <- glmer(ResponseIsTarget ~ 1 + cp1*l1 +
                     (1 + cp1 + l1 + cp1:l1 || Item) +
                     (1 + cp1 + l1 + cp1:l1 || Participant),
                 data = data,
                 control = glmerControl(calc.derivs=FALSE),
                 family="binomial",
                 na.action = na.omit
                 )
summary(model)
```

Time for plots and tables!!!
```{r}
grouped_data <- data %>% 
  group_by(Item, cp1, l1) %>%
  summarise(percentTarget = sum(ResponseIsTarget) / length(ResponseIsTarget),
            )
summary(grouped_data)
```
We'll use the percentage of responses which equaled the target for each
condition.

```{r}
grouped_data.SE <- summarySE(
  data = grouped_data, 
  measurevar = 'percentTarget',
  groupvars = c('cp1','l1'))

grouped_data.SE = grouped_data.SE %>%
  mutate(Location = case_when(
    l1 == -0.5 ~ 'Related',
    l1 == 0.5 ~ 'Unrelated',
  )) %>%
  mutate(ClausePlacement = case_when(
    cp1 == -0.5 ~ 'Leading',
    cp1 == 0.5 ~ 'Intervening'
  ))

# first, a bar chart
ggplot(grouped_data.SE, aes(x = Location,y = percentTarget,fill=Location)) +
  geom_bar(stat = "identity") +
  scale_fill_manual(values = c('#00A36C','#BBA53D')) +
  labs(title = 'Percentage of Responses Equal to Target by Clause Placement and Location',
       y = 'Percentage equal to Target'
  ) +
  theme(plot.title = element_text(hjust = 0.5), legend.position="none") + 
  facet_grid(~ClausePlacement) + 
  geom_errorbar(aes(ymin = percentTarget - se, ymax = percentTarget + se), 
                width = 0.1, 
                size = 0.5)

ggplot(grouped_data.SE, 
       aes(x = Location, 
           y = percentTarget, 
           group=ClausePlacement, 
           color = ClausePlacement)
       ) +
  geom_line() +
  geom_point() + 
  scale_color_manual(values = c('coral1','darkturquoise'),name = 'Clause Placement') +
  labs(title = 'Percentage of Responses Equal to Target by Clause Placement and Location',
       y = 'Percentage equal to Target'
  ) +
  geom_errorbar(aes(ymin = percentTarget - se, ymax = percentTarget + se), 
                width = 0.1, 
                size = 0.5)
  
```
We create two plots based on the grouped data.

```{r}
grouped_data.SE
```
