
```{r}
knitr::opts_chunk$set(echo = TRUE)
suppressPackageStartupMessages(library(dplyr))

data <- read.csv('../data/PreprocessedData.csv')
data$ClausePlacement <- as.factor(data$ClausePlacement)
data$Location <- as.factor(data$Location)
summary(data)
```
The data has the following columns:

Participants: the hash of the subject' IP address (used to identify them)
Item: the item number (1-80)
Condition: the condition (A, B, C, D)
  A = Beginning, Original
  B = Middle, Original
  C = Beginning, Replacement
  D = Middle, Replacement
Response: the subject's completion
ClausePlacement: is the dependent clause at the Beginning or in the Middle 
  i.e. intervening between the subject and the verb?
Location: is the subjects' location the Original location or the Replacement
  location?

```{r}
data %>%
  group_by(Item, ClausePlacement, Location) %>%
  count(Response) 
  # get counts of unique responses for each Item - ClausePlacement - Location
```
The first Item is sufficient to illustrate the problem, so we can disregard the 
rest.
---Our initial plan---
Our initial plan was to get the cloze probability of the most common word in the 
A condition ( = Beginning, Original) and compare the probability with the same
words probability in the other conditions.
For example, if 'pause' was the most common word in 1A with a cloze probability
of 70%, we would calculate the cloze probability of 'pause' in the 1B, 1C and 1D 
conditions. Then, we would compare difference between those probabilities and 
the probability of 'pause' in 1A. For example, if we have probabilities
  1A: P('pause') = 70%
  1B: P('pause') = 30%
  1C: P('pause') = 40%
  1D: P('pause') = 50%
we would calculate the differences 
  1A: 0%
  1B: -40%
  1C: -30%
  1D: -20%
That difference in cloze probability would be our response variable. In other
words, our formula (omitting random effects) would be
  DifferenceInCloze ~ ClausePlacement * Location
---The problem---
Unfortunately, we ran into a significant problem: for many items, all 
completions were equally common. For example, in 1A, 'pause','replace' and 
'think' were all provided once. Accordingly, we can't pick out a most probable
completion. 
We could, of course, just take the first alphabetically (here, it would be 
'pause') or use our target word. However, unless we do that one of those, 
the approach I described above won't work.
---Our question--- 
Is there any way we can quantify the difference between probability 
distributions and use that quantity as our response variable? That is, our 
formula (again omitting random effects) would be 
  DifferenceBetweenDistributions ~ ClausePlacement * Location
If that isn't workable or isn't desirable, what should we use as our response 
variable? Sorry if any of this was unclear or we misunderstood something.


